Model Based Analysis of Patient Derived Xenograft Tumor Volumes

### 2022-04-21 presentation_Kuhlers.Rmd
presentation

---
title: "Analysis of PDX Growth Data"
author: "Peyton Kuhlers"
date: "3/2/2022"
output: 
  beamer_presentation:
    theme: "AnnArbor"
---

@@

\note{Lots of ignored data, not modelling the entire time course}
\note{Plus multiple clusters, mouse, patient, etc}

@@

\centering
\includegraphics[width = 9cm, height = 5.5cm]{figures/growth_plots.pdf}

@@

\centering
$E[Y_{i}|b_i] = \beta_0 + b_{i1} + \beta_1(time_{i}) + b_{i2}(time) + \gamma_i (agent_i*time)$

>>>>

---
title: "Model Based Analysis of Patient Derived Xenograft Tumor Volumes"
author: "Peyton Kuhlers"
date: "4/25/2022"
output: beamer_presentation
---

@@

@@

- Mice are randomized to treatments and 'staged' to 150-200mm^3.

- 
\centering
\includegraphics[width = 9cm, height = 5.5cm]{figures/growth_plots.pdf}

@@

\centering
$log(E[Y_{i}|b_i]) = \beta_0 + b_{i1} + \beta_1(time_{i}) + b_{i2}(time) + \gamma_i (agent_i*time)$
